Developing Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set

### 2023-08-27 paper.tex
Update Appendix

A early proof-of-concept for a generalized address clustering Python module can be found under the following link:

\texttt{\url{}}

>>>>

An early version of a generalized address clustering Python module can be found at:

\texttt{\url{https://github.com/dariothuerkauf/intra-set-address-clustering}}

This module fetches the required data from Etherscan and Polygonscan when given a set of addresses as input, applies the Role2Vec algorithm to the resulting intra-set asset transfer data, and then constructs the clusters using a Euclidean Distance threshold. Please note that this module is still under development.
